\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\signature{Yongjun Kim \\ Department of Software, Ajou University \\ Suwon 16499, Republic of Korea \\ Email: yjkim0123@ajou.ac.kr}

\address{Yongjun Kim \\ Department of Software \\ Ajou University \\ Suwon 16499, Republic of Korea}

\begin{document}

\begin{letter}{Editor-in-Chief \\ IEEE Access}

\opening{Dear Editor,}

We are pleased to submit our manuscript entitled \textbf{``Unsupervised Anomaly Detection in Hospital Financial Statements: A Multi-Algorithm Consensus Approach with Explainable AI''} for consideration for publication in \textit{IEEE Access}.

This paper proposes a multi-algorithm consensus framework for unsupervised anomaly detection in hospital financial statements. Unlike supervised approaches that require labeled datasets---an assumption rarely met in healthcare financial surveillance---our framework combines five complementary unsupervised algorithms (Isolation Forest, Local Outlier Factor, One-Class SVM, DBSCAN, and autoencoder) and identifies ``strong anomalies'' flagged by three or more methods.

Key contributions include:

\begin{itemize}
\item A consensus mechanism that reduces false positives inherent in any single algorithm while capturing diverse notions of abnormality, yielding 57 consensus anomalies (6.9\%) from a balanced panel of 165 Korean hospitals over 2019--2023 ($N = 827$).
\item Statistical validation showing that consensus anomalies exhibit significantly higher labor cost ratios, administrative cost ratios, and subsidy dependence ($p < 0.001$ for all).
\item SHAP-based explainability analysis on the Isolation Forest model, identifying hospital ownership type, subsidy ratio, and administrative costs as primary drivers of anomaly scores.
\item A key finding that only 47.4\% of consensus anomalies overlap with accounting-deficit hospitals ($\chi^2 = 0.67$, $p = 0.414$), demonstrating that unsupervised anomaly detection captures structurally unusual financial patterns beyond simple profitability.
\end{itemize}

We believe this work is well-suited for \textit{IEEE Access} because it bridges unsupervised machine learning methodology with healthcare financial surveillance, providing a practical tool for regulators. The framework is algorithm-agnostic and generalizable to other organizational financial monitoring settings.

This manuscript has not been published previously, is not under consideration for publication elsewhere, and its publication is approved by all authors. The authors declare no conflicts of interest.

Analysis code is publicly available at: \url{https://github.com/yjkim0123/hospital-anomaly-detection}.

\closing{Sincerely,}

\end{letter}
\end{document}
